Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-09-08 limits/ms.tex
rearranged action items

The main results from modelling these different configuration are shown in black in
\figref{main results}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of `quality' of recovery, defined as: 
\begin{equation}
\chi^2 = \frac
       {\Big\langle \int \left|\Delta\Sigma(\vec{\theta})\right|^2 \,
        d^2 \vec{\theta} \Big\rangle}
       {\int \Sigma^2(\vec{\theta}) \; d^2 \vec{\theta}}
\end{equation}
where the angle brackets denote averages over the model ensemble.
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

@@

{\bf JR. ACTION ITEMS.

@@

\item Jonathan to complete \S\ref{sec:glass}. Emphasise need for central adaptive grid. Add appendix showing convergence as Pixrad is increased.

\item Jonathan to write section \S\ref{sec:glassextraimages} on removing models with extra images.

@@

\item Add appendix showing how ``radial symmetry" prior affects results. Clarify meaning of this prior with a nice figure showing the symmetry.

\item Show results for $1\sigma$ and $2\sigma$ rather than full \Glass\ ensemble. Add results for Claudio's shape measure. Discuss shape throughout results section and mention more explicitly in abstract and conclusions -- what quality of data do we need to robustly constrain the shape?

\item Add example plot of the projected density and recovered projected density (c.f. plots Jonathan made for my ERC proposal).

\item Tidy up figures and other small items as detailed throughout -- see {\tt {\bf JR ... }}.

\item Change variable chi to something else ($f$?) to avoid confusion
  with $\chi^2$.

\item Replace equation 20 with what you are actually doing when
  calculating $chi$ (now $f$).

\item Add plot of $chi$ ($f$) for $lambda_1/lambda_2$ and theta shape
  parameters (c.f. what Claudio is doing).

\item Calculate aperture averaged $\sigma$ to 2 (or 3 you decide) half
  light radii assuming $beta = 0$ for a model (double) where the mass
  is poorly constrained by strong lensing. Accept/reject models from
  the ensemble $\Longrightarrow$ what we learn from combined lensing
  kinematics.

\end{enumerate} 
}

>>>>

The main results from modelling these different configuration are shown in black in
\figref{main results}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of `quality' of recovery, defined as: 
\begin{equation} \label{badness}
\chi^2 = \frac
       {\Big\langle \int \left|\Delta\Sigma(\vec{\theta})\right|^2 \,
        d^2 \vec{\theta} \Big\rangle}
       {\int \Sigma^2(\vec{\theta}) \; d^2 \vec{\theta}}
\end{equation}
where the angle brackets denote averages over the model ensemble.
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

@@

Various action items.

\subsection{Goodness of recovery}

@@

\item Change variable $\chi$ to something else ($f$?) to avoid
  confusion with $\chi^2$.

\item Correct equation \eqref{badness} to describe what is actually
  calculated.

\item Show results for $1\sigma$ and $2\sigma$ rather than full
  \Glass\ ensemble.

\item Add results for Claudio's shape measure. Discuss shape
  throughout results section and mention more explicitly in abstract
  and conclusions -- what quality of data do we need to robustly
  constrain the shape?

\item Add plot of $\chi$ ($f$) for $lambda_1/lambda_2$ and shape
  parameters (cf. what Claudio is doing).

\end{enumerate}

\subsection{Kinematics}

\item Add example plot of the projected density and recovered
  projected density (cf. plots Jonathan made for Justin's ERC
  proposal).

\item Calculate aperture averaged $\sigma$ to 2 (or 3 you decide) half
  light radii assuming $\beta = 0$ for a model (double) where the mass
  is poorly constrained by strong lensing. Accept/reject models from
  the ensemble $\Longrightarrow$ what we learn from combined lensing
  kinematics.

\end{enumerate}

\subsection{Other}

\item Tidy up figures and other small items as detailed throughout --
  see {\bf JR ... }

\item Add appendix showing how inversion symmetry in the prior affects
  results. Clarify meaning of this prior with a nice figure showing
  the symmetry.

\item Complete \S\ref{sec:glass}. Emphasise need for central adaptive
  grid. Add appendix showing convergence as Pixrad is increased.

\end{enumerate}

\subsection{Clarifications in text}

\item Write section \S\ref{sec:glassextraimages} on removing models
  with extra images.

@@

\end{enumerate}
